Robustly decorrelating errors with mixed quantum gates

### 2019-06-18 decorrelation/mixed_unitaries.tex
Addded ASCR statement

\documentclass[aps,nofootinbib,pra,notitlepage,twocolumn]{revtex4-1}
\usepackage{amsfonts,amsmath,amssymb,amsthm}
 \usepackage{array,bm,color}
\usepackage{epsfig,graphicx,nomencl,revsymb4-1,upgreek,url}
\usepackage{hyperref}
\usepackage{algorithm}
\usepackage{algpseudocode}
\usepackage{graphicx}
\usepackage{calc}
\usepackage{tabularx}
\newcolumntype{Y}{>{\centering\arraybackslash}X}
\graphicspath{{./figures/}}
\hypersetup{colorlinks=true, pdfauthor=Anthony M. Polloreno, pdftitle=Advantages of mixed quantum gates for information processing, citecolor=blue, linkcolor=blue}
\newcommand{\tr}{{\rm Tr\thinspace}}
\newcommand{\bra}[1]{\ensuremath{\left\langle{#1}\right\vert}}
\newcommand{\ket}[1]{\ensuremath{\left\vert{#1}\right\rangle}}
\newcommand{\braket}[2]{\left\langle #1 | #2 \right\rangle}
\newcommand{\ketbra}[2]{\left| #1 \right\rangle\!\!\!\,\left\langle #2 \right|}
\newcommand{\abs}[1]{\left\vert #1 \right\vert}
\newcommand{\expect}[1]{\ensuremath{\left\langle{#1}\right\rangle}}
\newcommand{\timeorder}{\ensuremath{\underset{\leftarrow}{\mathcal{T}}}}
\newcommand{\ident}{{\mathbb1}}
\newcommand{\order}[1]{\mathcal{O}\left( #1 \right)}
\newcommand{\diag}[1]{\mathrm{diag}\{#1\}}
\newcommand{\trans}[1]{#1^\mathsf{T}}
\newcommand{\T}{\mathsf{T}}
\newcommand{\erf}[1]{Eq.~(\ref{#1})}
\newcommand{\needcite}{{\color{blue}\textsuperscript{[citation needed]}}}
\newcommand{\note}[1]{{\color{red}[#1]}}
\newcommand{\kcy}[1]{{\color{red}[#1]_{\rm{KCY}}}}
\newcommand{\amp}[1]{{\color{red}[#1]_{\rm{AMP}}}}
\newcommand{\deriv}[0]{{\frac{d}{d\vec{\delta}}}}

@@

\section{Acknowledgements}
\label{sec:acknowledgements}
Sandia National Laboratories is a multimission laboratory managed and operated by National Technology and Engineering Solutions of Sandia, LLC, a wholly owned subsidiary of Honeywell International, Inc., for the U.S. Department of Energy's National Nuclear Security Administration under contract DE-NA0003525.
\bibliography{mixed_unitaries.bib}

>>>>

\documentclass[aps,nofootinbib,pra,notitlepage,twocolumn]{revtex4-1}
\usepackage{amsfonts,amsmath,amssymb,amsthm}
 \usepackage{array,bm,color}
\usepackage{epsfig,graphicx,nomencl,revsymb4-1,upgreek,url}
\usepackage{hyperref}
\usepackage{algorithm}
\usepackage{algpseudocode}
\usepackage{graphicx}
\usepackage{calc}
\usepackage{tabularx}
\newcolumntype{Y}{>{\centering\arraybackslash}X}
\graphicspath{{./figures/}}
\hypersetup{colorlinks=true, pdfauthor=Anthony M. Polloreno, pdftitle=Advantages of mixed quantum gates for information processing, citecolor=blue, linkcolor=blue}
\newcommand{\tr}{{\rm Tr\thinspace}}
\newcommand{\bra}[1]{\ensuremath{\left\langle{#1}\right\vert}}
\newcommand{\ket}[1]{\ensuremath{\left\vert{#1}\right\rangle}}
\newcommand{\braket}[2]{\left\langle #1 | #2 \right\rangle}
\newcommand{\ketbra}[2]{\left| #1 \right\rangle\!\!\!\,\left\langle #2 \right|}
\newcommand{\abs}[1]{\left\vert #1 \right\vert}
\newcommand{\expect}[1]{\ensuremath{\left\langle{#1}\right\rangle}}
\newcommand{\timeorder}{\ensuremath{\underset{\leftarrow}{\mathcal{T}}}}
\newcommand{\ident}{{\mathbb1}}
\newcommand{\order}[1]{\mathcal{O}\left( #1 \right)}
\newcommand{\diag}[1]{\mathrm{diag}\{#1\}}
\newcommand{\trans}[1]{#1^\mathsf{T}}
\newcommand{\T}{\mathsf{T}}
\newcommand{\erf}[1]{Eq.~(\ref{#1})}
\newcommand{\needcite}{{\color{blue}\textsuperscript{[citation needed]}}}
% \newcommand{\note}[1]{{\color{red}[#1]}}
\newcommand{\note}[1]{}
\newcommand{\kcy}[1]{{\color{red}[#1]_{\rm{KCY}}}}
\newcommand{\amp}[1]{{\color{red}[#1]_{\rm{AMP}}}}
\newcommand{\deriv}[0]{{\frac{d}{d\vec{\delta}}}}

@@

\section{Acknowledgements}
\label{sec:acknowledgements}
This material was funded in part by the U.S. Department of Energy, Office of Science, Office of Advanced Scientific Computing Research Quantum Testbed Program. Sandia National Laboratories is a multimission laboratory managed and operated by National Technology and Engineering Solutions of Sandia, LLC, a wholly owned subsidiary of Honeywell International, Inc., for the U.S. Department of Energy's National Nuclear Security Administration under contract DE-NA0003525.
\bibliography{mixed_unitaries.bib}
